A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-11-08 writedown/zm/paper.water/main.tex
merge with I.F., add my revise

\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}

\usepackage{amsmath,amssymb,amsfonts,latexsym}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{indentfirst} 
\usepackage{rotating,booktabs}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}            
\newcommand{\bluec}[1]{{\color{blue} #1}}            
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}

\begin{document}

\title{A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road 6, 100088 Beijing, China}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita, Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako, Saitama 351-0198, Japan}

@@

\maketitle

@@

\section{Zero-Multiple Method}

Introduction of the ZM method, formula...

\recheck{If we want to discuss the issue of cut-off method, a short
  introduction of the group cut-off v.s.~the atom cut-off
  method. (will discuss the implementation in gromacs later)}

\section{Benchmark quantities}

In order to investigate the performance of ZM method, we simulation
the water system by using both SPME and ZM methods, and calculate a set
of \emph{benchmark quantities}.  This set covers a broad range of
water properties that are of general interest. It includes the
structure property (radial distribution function), the thermodynamic
properties (pressure, excess chemical potential, constant
volume/pressure heat capacity, isothermal compressibility, thermal
expansion coefficient), dielectric properties (dielectric constant and
Kirkwood-G factor) and dynamical properties (diffusion constant and
viscosity).
The definitions and computing methods of these quantities are provided in details
in Appendix.~\ref{appendix:benchmark}.
By comparing ZM to SPME, a good consistency in computing
the benchmark quantities would indicate a good accuracy of the ZM
method.
More importantly, the benchmark tests provide knowledge in the
stituations when the ZM method does not work so well, and help in
finding the way of tuning the working parameters to achieve higher accuracy.
The ZM method is also compared to the traditional short-range method: RF.

\section{Simulation protocols}

In this work, we focus on the water system modeled by
TIP3P~\cite{jorgensen1983comparison} point-charge water model.
% Other point-charge water models differ in the modeling parameters, and
The accuracy of ZM method in other water models is out of the scope of the current work.
However, since the point-charge water models share similar idea, and  only differ
in the model parameters, it is highly probable that ZM works well with other water models if it works
well with TIP3P.

All simulations were performed by Gromacs~4.6.5~\cite{hess2008gromacs, pronk2013gromacs} complied by GNU C compiler with single-precision floating point.
The size of the systems and corresponding number of molecules used for MD simulations are summarized in Tab.~\ref{tab:tmp1}.
The benchmark quantities were calculated in either  canonical (NVT) or isothermal-isobaric (NPT) ensemble, with equilibrium temperature $T=300$~K.
In order to simulate at the desired temperature,
the systems $\systemsb$ and $\systemsbp$ were coupled to Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} thermostat with time-scale $\tau_T = 1.0$~ps,
while systems $\systemmb$, $\systemmbp$, $\systemla$, $\systemlb$ and $\systemlbp$ were coupled to Langevin thermostat with time-scale $\tau_T = 0.1$~ps.
In the NPT simulations, the systems were further coupled
to the Parrinello-Rahman barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs implementation)
with time-scale $\tau_P = 0.5$~ps to equilibriate the system at 1~Bar.
All systems were integrated with leap-frog scheme at a time-step of 0.001~ps.
The neighbor lists were updated every 5 time-steps.
The ``\texttt{group}'' cut-off scheme in Gromacs was used. In order to mimic the atomistic
cut-off manner, the radius for neighbor list building was set 0.3~nm
larger than the cut-off radius (the maximum of Coulomb cut-off and the van der Waals cut-off).
To make sure the van der Waals interactions were cut-off in a smooth way,
they are modified in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs ``\texttt{shift}'' method.
The ZM method was implemented in Gromacs with the tabulated electrostatic interaction. A home-made code was used to generate the interaction tables.
The short-range part of SPME method is smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
The reciprocal space
grid spacing is set to 0.06~nm, with B-Spline interpolation order of 6.
These parameters are chosen to be more accurate than the Gromacs default choices (grid spacing 0.12~nm and interpolation order 4).
The splitting parameter is optimized by the error estimate for the SPME method, which is implemented in Gromacs by tool ``\texttt{g\_pme\_error}''~\cite{wang2010optimizing}.
The optimized real space and reciprocal space force computing errors were equally distributed as $1.4\times10^{-4}$~kJ/(mol nm).
Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches the limit of the single-precision representation of the floating point numbers.
In the simulations of the RF method, the interactions were cut-off in the group manner,
so the radius for neighbor list building is set identical to the cut-off radius.
No cut-off smoothing of the electrostatic interaction was applied in the cases of RF simulation.

\begin{table}
  \centering
  \caption{A list of systems simulated in this work. We report, from left to right, the number of water
    molecules in the system (TIP3P model), equilibrium box size, length of equilibriation, length of productive trajectory.
  }
  \vskip .5cm
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c rrrr}\hline\hline
    System      & $N$ & $V$ [$\textrm{nm}^3$]  & $T_{\textrm{eq}}$ [ps] & $T_{\textrm{prod}}$ [ps]  \\\hline
    $\systemsbp$         &   2,500        & $4.24^3$              & --           &  6,000        \\
    $\systemsb$          & 2,500          & $4.24^3$              & 3,000        & 27,000        \\\hline
    $\systemmbp$         &   4,500        & $5.15^3$              & --           &  6,000        \\
    $\systemmb$          & 4,500          & $5.15^3$              & 3,000        & 17,000        \\\hline
    $\systemla$          &   13,824       & $7.49^3$              & 200          & 1,800         \\
    $\systemlbp$         &   13,824       & $7.49^3$              & --           & 10,000        \\
    $\systemlb$          &   13,824       & $7.49^3$              & 3,000        & 17,000        \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp1}
\end{table}

The initial configurations were prepared by in
the following steps:
(1) An NPT simulation of system $\systemla$ with SPME
electrostatic was performed. The equilibrium density (984.1~$\textrm{kg}/\textrm{m}^{3}$) of the system is calculated
from this simulation.
(2) Initial configurations that contains 2500, 4500 and
13824 molecules were generated at the calculated equilibrium
density.
(3) NVT simulations with SPME electrostatic for system $\systemsbp$, $\systemmbp$
and $\systemlbp$ are performed.
(4) The output configurations of $\systemsbp$ and $\systemmbp$ were used as
initial configurations for system $\systemsb$ and $\systemmb$, respectively.  The output configuration of
$\systemlbp$ was used as initial configurations for system $\systemla$ and $\systemlb$.
% The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.

@@

The smallest system $\systemsb$ was adopted,
because for the quantities that are computed  by estimating fluctuations (in this
work heat capacities, compressibility, thermal expansion coefficient, dielectric constant, diffusion constant and
viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}), simply increase the size of the
system does not improve the accuracy of the 
simulation~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
The optimal way of measuring these properties
is to simulate with smaller systems
% (as far as the finite size effect is negligible)
and run longer simulations for longer time-averages.
The reason of using Nose-Hoover thermostat is that
it perturbs the dynamics of the system only slightly, while the
Langevin thermostat is likely to substantially change the dynamics
when the coupling is very strong, therefore, the former was used in computing the dynamical
properties like the diffusion constant and viscosity.
The quantities that
are ensemble averages (in this work, pressure, chemical potential, radial distribution function and Kirkwood-G factor are of this type)
were computed by the largest system $\systemlb$,
in order to achieve higher parallel efficiency.
The system $\systemmb$ is simulated to investigate the size-dependency of the
Kirkwood-G factor~\cite{vanderSpoel2006origin}.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    The ZM methods with order from 1 to 4 are compared with the RF. 
    The splitting parameter of ZM method is set to be $\alpha = 0.00\,\textrm{nm}^{-1}$.
    The black solid line indicates the magnitude  of the correct pressure: 1~Bar.
    The error bars present the statistical uncertainty at 95\% confidence level.
  }
  \label{fig:pres-comp}
\end{figure}

The equilibrium density of the system was determined by an NPT SPME
simulation.  Then using this density in the NVT simulation with SPME electrostatic, the
pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of
1.0~Bar, which means the system is in desired thermodynamic state.  The accuracy of ZM method, can be investigate by checking if
the NVT pressure is consistent with the target pressure, when the SPME equilibrium density is used.  In
Fig.~\ref{fig:pres-comp}, the pressure calculated by ZM method of
order $l=1,2,3$ and 4 are plotted against the cut-off radius.
All the  simulations are done with system $\systemla$.
It is concluded from the Figure that all ZM methods converges to the
target pressure at large enough cut-off radius.
In general, the higher order of ZM presents an larger error in the pressure calculation than
the lower order ZM method.
Higher order are also more sensitive in the  cut-off radius dependency.
ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$ and 4 tends to over-estimate.
The ZM method is also compared with
the RF method using the experimental dielectric constant $\varepsilon_{\textrm{rf}} = 80$, 
from which it is concluded that the accuracy of ZM in pressure calculation is much higher
than the RF method.
It should be noted that even with the largest system of 13824 water molecules,
the fluctuation (measured by standard deviation) of the pressure is roughly 100~Bar, which means that it is
very difficult achieve very accurate estimate for this quantity. In practice a pressure error of 20~Bar is
still acceptable.

\begin{figure}
  \centering
  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l1.eps}
  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}
  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
  \caption{The pressure convergence with respect to the cut-off radius
    for ZM methods with  splitting parameter from $0.0$ to $2.0\,\textrm{nm}^{-1}$.
    From left to right, up to down presents the ZM method of order 1 to 4.
    The black solid line indicates the magnitude  of the correct pressure: 1~Bar.
    The error bars present the statistical uncertainty at 95\% confidence level.
  }
  \label{fig:pres-l1}
\end{figure}

The effect of using different splitting parameter on the convergence
of the pressure is investigate in Fig.~\ref{fig:pres-l1}.
In general, the higher order indicates less significant dependency on the splitting parameter.
In the case of $l=1$, the splitting parameter 0.0 is consistent with  $0.5\,\textrm{nm}^{-1}$, and
by using higher splitting parameter, the pressure shifts to the higher pressure side.
For $l=2,3$ and 4, the convergence is not sensitive to $\alpha$ up to  $1.0\,\textrm{nm}^{-1}$.
More importantly,  by using $\alpha = 1.5$ or $2.0\,\textrm{nm}^{-1}$,
the pressure does not converges to the desired value 1~Bar. Therefore, the high splitting parameter
is not suggested in the simulations where the high pressure accuracy is important.

>>>>

%2multibyte Version: 5.50.0.2952 CodePage: 932
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}

\documentclass[a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsfonts,latexsym}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{indentfirst}
\usepackage{rotating,booktabs}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Friday, November 07, 2014 19:42:26}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}
% \input{tcilatex}
\begin{document}

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}

@@

\maketitle
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}

% A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation}

@@

[{\color{blue} COMMENT: I can contribute this section later}]

\section{Zero-Multipole Summation}

Introduction of the ZM method, formula...[ {\color{blue} COMMENT: I can
write here later}]

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? \recheck{I mean the explanation of group and atomistic cut-off method. the traditional gromacs uses gropu cut-off as default. We need instead the atomistic cut-off}}]

\section{Material and Methods}

\subsection{Benchmark quantities}

In order to investigate the performance of ZM method, we simulate the water
system by using both SPME and ZM methods, and evaluate a set of \emph{%
benchmark quantities}. This set covers a broad range of water properties
that are of general interest. It includes the structure property (radial
distribution function), the thermodynamic properties (pressure, excess
chemical potential, constant volume/pressure heat capacity, isothermal
compressibility, thermal expansion coefficient), dielectric properties
(dielectric constant and Kirkwood-G factor) and dynamical properties
(diffusion constant and viscosity). The definitions and computing methods of
these quantities are provided in details in Appendix.~\ref%
{appendix:benchmark}. By comparing ZM to SPME, a good consistency in
computing the benchmark quantities would indicate a good accuracy of the ZM
method. More importantly, the benchmark tests provide knowledge in the
situations when the ZM method does not work so well, and help in finding the
way of tuning the working parameters to achieve higher accuracy. The ZM
method is also compared to the traditional short-range method: RF.

\subsection{Simulation protocols}
\label{sec:protocols}
In this work, we focus on a system of water molecules modeled
by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
% Other point-charge water models differ in the modeling parameters, and
The accuracy of ZM method in other water models is out of the scope of the
current work. However, since the point-charge water models share similar
idea, and only differ in the model parameters, it is highly probable that ZM
works well with other water models if it works well with TIP3P.

All simulations were performed by Gromacs~4.6.5~\cite{hess2008gromacs,
pronk2013gromacs} complied by GNU C compiler with single-precision floating
point. The size of the systems and corresponding number of molecules used
for MD simulations are summarized in Tab.~\ref{tab:tmp1}. The benchmark
quantities were calculated in either canonical (NVT) or isothermal-isobaric
(NPT) ensemble, with equilibrium temperature $T=300$~K. In order to simulate
at the desired temperature, the systems $S_{1}$ and $S_{1}^{\prime }$ were
coupled to Nos\'{e}-Hoover~\cite{nose1984molecular,hoover1985canonical}
thermostat with time-scale $\tau _{T}=1.0$~ps, while systems $M_{1}$, $%
M_{1}^{\prime }$, $L_{0}$, $L_{1}$ and $L_{1}^{\prime }$ were coupled to
Langevin thermostat with time-scale $\tau _{T}=0.1$~ps. In the NPT
simulations, the systems were further coupled to the Parrinello-Rahman
barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs
implementation) with time-scale $\tau _{P}=0.5$~ps to equilibrate the system
at 1~Bar. All systems were integrated with leap-frog scheme at a time-step
of 0.001~ps.

The neighbor lists were updated every 5 time-steps. The \textquotedblleft 
\texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used. In
order to mimic the atomistic cut-off manner, the radius for neighbor list
building was set 0.3~nm larger than the cut-off radius (the maximum of
Coulomb cut-off and the van der Waals cut-off). [ {\color{blue} COMMENT:
Yes,..., this is not easy to understand how we mimic AC. \recheck{it should be OK as it is now.}}] To make sure the
van der Waals interactions were cut-off in a smooth way, they are modified
in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs
\textquotedblleft \texttt{shift}\textquotedblright\ method.

The short-range part of SPME method \recheck{was cut-offed at 1.9~nm, and was} smoothed in a shell of $0.05$~nm
width by the Gromacs \textquotedblleft \texttt{pme-switch}%
\textquotedblright\ method. The reciprocal space grid spacing was set to
0.06~nm, with B-Spline interpolation order of 6. These parameters were
chosen to be more accurate than the Gromacs default choices (grid spacing
0.12~nm and interpolation order 4). The splitting parameter was optimized by
the error estimate for the SPME method, which is implemented in Gromacs by
tool \textquotedblleft \texttt{g\_pme\_error}\textquotedblright ~\cite%
{wang2010optimizing}. The optimized real space and reciprocal space force
computing errors were equally distributed as $1.4\times 10^{-4}$~kJ/(mol
nm). Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm),
this force computing precision almost reaches the limit of the
single-precision representation of the floating point numbers.

In the simulations of the RF method, the interactions were cut-off in the
group manner, so the radius for neighbor list building is set identical to
the cut-off radius. No cut-off smoothing of the electrostatic interaction
was applied in the cases of RF simulations. We used $1.2$~nm
cut-off and the experimental dielectric constant $\varepsilon _{\textrm{rf}}=80$.

The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction. A home-made code was used to generate the interaction tables.

\begin{table}[tbp]
\caption{A list of systems simulated in this work. We report, from left to
right, the number of water molecules in the system (TIP3P model),
equilibrium box size, length of equilibriation, length of productive
trajectory. }
\label{tab:tmp1}\centering
\vskip .5cm 
\begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}crrrr}
\hline\hline
System & $N$ & $V$ [$\text{nm}^3$] & $T_{\text{eq}}$ [ps] & $T_{\text{prod}}$
[ps] \\ \hline
$S^{\prime }_1$ & 2,500 & $4.24^3$ & -- & 6,000 \\ 
$S_1$ & 2,500 & $4.24^3$ & 3,000 & 27,000 \\ \hline
$M^{\prime }_1$ & 4,500 & $5.15^3$ & -- & 6,000 \\ 
$M_1$ & 4,500 & $5.15^3$ & 3,000 & 17,000 \\ \hline
$L_0$ & 13,824 & $7.49^3$ & 200 & 1,800 \\ 
$L^{\prime }_1$ & 13,824 & $7.49^3$ & -- & 10,000 \\ 
$L_1$ & 13,824 & $7.49^3$ & 3,000 & 17,000 \\ \hline\hline
\end{tabular*}%
\end{table}

The initial configurations were prepared by in the following steps: (1) An
NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
calculated from this simulation. (2) Initial configurations that contains
2500, 4500 and 13824 molecules were generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system $%
S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$
were used as initial configurations for system $S_{1}$ and $M_{1}$,
respectively. The final configuration of $L_{1}^{\prime }$ was
used as initial configurations for system $L_{0}$ and $L_{1}$. % The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.
% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
%   special care, please modify.}]
Using the density in the NVT simulation with
SPME electrostatic, the pressure ($-0.4\pm 1.5$~Bar) is reproducing the
target pressure of 1.0~Bar, which means the system is in desired
thermodynamic state.

@@

The smallest system $S_{1}$ was adopted for the quantities that are computed
by estimating fluctuations (in this work heat capacities, compressibility,
thermal expansion coefficient, dielectric constant, diffusion constant and
viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}%
), because simply increasing the size of the system does not
improve the accuracy of the simulation~\cite%
{milchev1986fluctuations,ferrenberg1991statistical}. The optimal way of
measuring these properties is to simulate with smaller systems 
% (as far as the finite size effect is negligible)
and run longer simulations for longer time-averages. The reason of using Nos%
\'{e}-Hoover thermostat is that it perturbs the dynamics of the system only
slightly, while the Langevin thermostat is likely to substantially change
the dynamics when the coupling is very strong, therefore, the former was
used in computing the dynamical properties like the diffusion constant and
viscosity. The quantities that are ensemble averages (in this work,
pressure, chemical potential, radial distribution function and Kirkwood-G
factor are of this type) were computed by the largest system $L_{0}$ or $L_{1}$, in order to
achieve higher parallel efficiency. The system $M_{1}$ is simulated to
investigate the size-dependency of the Kirkwood-G factor~\cite%
{vanderSpoel2006origin}.

@@

\begin{sidewaystable}
  \centering
  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
    thermal expansion coefficient $\alpha_V$
    calculated by different methods.    
    The parentheses in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \bigskip
  \centering\small\setlength\tabcolsep{2pt}
  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha_V$ &  $\eps$ & $D$ &  $\eta$  \\
                & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
                &    &    &    &NVT $\systemla$&NVT $\systemsb$&  NPT $\systemsb$          &  NPT $\systemsb$    &  NPT $\systemsb$    & NVT $\systemsb$& NVT $\systemsb$    & NVT $\systemsb$       \\\hline
    SPME        &1.9 & -- &2.1 & $-26.1$ (0.2) & 72.2 (1.0)  &79.2 (0.9)           & 5.94 (0.05)               &1.03 (0.02)          & 98 (3)          &         5.86  (0.07)&         0.315  (0.007)\\
    RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
    ZM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
    ZM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
    ZM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
    ZM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
    ZM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
    ZM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
    ZM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
    ZM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:thermo}
\end{sidewaystable}

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors.
The dependence of the ZM results on the order\ $l$\ is \recheck{little}.
Although the splitting parameter, $\alpha $, also does not have significant
influence on almost all these thermodynamic quantities for $l=1$, only the
isothermal compressibility admits a weak dependence [\recheck{all except $\alpha=2$ are in the statistical uncertainty, by which we cannot say $\alpha=1$ is optimal... I remove ``and $\alpha=1$ seems optimal''}].
Overall, the ZM\ agrees with the SPME results without any bias and
out-performs the RF.

\recheck{
  It should be noticed that in the calculation of the chemical potential,
  the energy correction plays an important role. In the case of $l=1$, $\alpha = 0.0\,\text{nm}^{-1}$,
  it contributes $-0.1$~kJ/mol to the final result.
  By increasing $l$ or $\alpha$, this contribution
  becomes more significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha = 0.0\,\text{nm}^{-1}$, and
  $-1.0$~kJ/mol for $l=1$, $\alpha = 2.0\,\text{nm}^{-1}$, respectively.
}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level.
\recheck{This uncertainty is twice of the standard deviation of the estimates (which are averages along MD trajectories) that
is calculated by the block average method~\cite{janke2002statistical}.}
}
\label{fig:pres-comp}
\end{figure}

We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
pressure, simulated with system $L_{0}$. The pressure calculated by ZM
method of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
method are plotted in Fig.~\ref{fig:pres-comp}. All ZM methods converges to
the target pressure at large enough cut-off radius. Lower order ZM presents
an smaller error in the pressure calculation than the higher order ZM
method. Note ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$
and 4 tends to over-estimate. However, the accuracy of ZM in pressure
calculation is much higher than that of the RF method.

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l1.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}%
% \newline
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
\caption{
The pressure convergence with respect to the cut-off radius for ZM
method $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$. The black
solid line indicates the magnitude of the correct pressure: 1~Bar. The error
bars present the statistical uncertainty at 95\% confidence level.}
\label{fig:pres-l1}
\end{figure}

The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
=0$ and shows good convergence. However, a higher $\alpha $ shifts the
pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1$
should be used in the simulations where the high accuracy in the pressure is
important. This "anti-damping effect" is similarly seen in the energy
accuracy in the TIP3P model~\cite{fukuda2014zero}.
% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
In SI the results of the higher order are shown, which are similar to that
of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not sensitive to $%
\alpha $ up to $1.0\,\text{nm}^{-1}$.

\recheck{It should be noted that even with the system $L_0$ that contains 13824 water molecules}, the
fluctuation (measured by standard deviation) of the pressure is roughly
100~Bar, which means that it is very difficult to achieve very accurate
estimate for this quantity. In practice a pressure error of 20~Bar is still
acceptable.
